### 2018-06-07 README.Rmd
final revision

> Bicho, N. and Cascalheira, J.. _The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory_. Short-term occupations in Paleolithic Archaeology

@@

> Bicho, N. and Cascalheira, J., (2018). _The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

> Bicho, N. and Cascalheira, J. (Accepted) _The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory_. In Picin, A. and Cascalheira, J. (eds.) Short-term occupations in Paleolithic Archaeology. Interdisciplinary Contributions to Archaeology. Springer.

@@

> Bicho, N. and Cascalheira, J., (2018). _The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory_. SocArXiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/3WGSA>
